A primer to numerical simulations: The perihelion motion of Mercury

### 2017-12-07 tex/MercuryNumerical.tex
author list: todo source files (license) and citations for urls

\author{I. Hammer, C. Hanhart, C. Körber and C. Müller}

\address{Forschungszentrum Jülich}
\ead{c.hanhart@fz-juelich.de}
\vspace{10pt}
%\begin{indented}
%\item[]February 2014
%\end{indented}

>>>>

\author{
	C.~Körber$^{1}$,
	I.~Hammer$^{1}$,
	??$^{3}$,
	J.-L.~Wynen$^{1}$,
	C.~Müller$^{2}$ and 
	C.~Hanhart$^{1}$
}
\address{
	$^1$ \textit{Institute für Kernphysik and Institute for Advanced Simulations, Forschungszentrum Jülich, D-52425 Jülich, Germany}\\
	$^2$ \textit{??}\\
	$^2$ \textit{??}
}
\ead{c.koerber@fz-juelich.de, c.hanhart@fz-juelich.de}
\vspace{10pt}
%\begin{indented}
%\item[]February 2014
%\end{indented}
